A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-11 src/tex/ms.tex

\section{Methods}
\label{sec:methods}

@@

We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the {\tt yZ1} and {\tt yZ2} yield sets, respectively, to ensure our models could reach ${\rm [O/Fe]}\approx0.0$ by the end time. The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\bar m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009} \todo{(are there more recent citations?)}. The rate for the {\tt yZ1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies. The rate for the {\tt yZ2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}.

@@

\subsection{Observational Sample}
\label{sec:observational-sample}

@@

\subsection{The SN Ia Delay-Time Distribution}
\label{sec:dtd-discussion}

>>>>

\section{Observational Sample}
\label{sec:observational-sample}

\section{Chemical Evolution Models \& Parameter Selection}
\label{sec:methods}

@@

We increased $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\% for the {\tt yZ1} and {\tt yZ2} yield sets, respectively, to ensure our models could reach ${\rm [O/Fe]}\approx0.0$ by the end time. The final row of Table \ref{tab:yields} reports the integrated SN Ia rate $N_{\rm Ia}/M_\star$ from each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009} \todo{(are there more recent citations?)}. The rate for the {\tt yZ1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies. The rate for the {\tt yZ2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}.

@@

@@

% \subsection{The SN Ia Delay-Time Distribution}
% \label{sec:dtd-discussion}
